---
title: "Portfolio Construct & Performance Analysis"
output:
  pdf_document: default
  html_document: default
date: "6/27/2018"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(repos="https://cran.rstudio.com" )
```

## Construct optimal portfolio

```{r car}
library(readr)
stocks <- read_csv("/Users/yuning/Documents/T3/Portfolio Management/stocks.csv", 
                         col_types = cols(ACA = col_number(), 
                                                     ACA_return = col_number(), AD = col_number(), 
                                                    AD_return = col_number(), BB = col_number(), 
                                                    BB_return = col_number(), BM = col_number(), 
                                                    BM_return = col_number(), CAI = col_number(), 
                                                    CAI_return = col_number(), Dates = col_date(format = "%m/%d/%Y"), 
                                                    ENX = col_number(), ENX_return = col_number(), 
                                                    GFC = col_number(), GFC_return = col_number(), 
                                                    HBRN = col_number(), HBRN_return = col_number(), 
                                                    KCR = col_number(), KCR_return = col_number(), 
                                                    STREV = col_number(), STREV_return = col_number(), 
                                                    UPM = col_number(), UPM_return = col_number()))
View(stocks)
```

compute correlation and covariance of each stock in the portfolio

```{r pressure, echo=FALSE}
#compute correlation and covariance
library(ggcorrplot)
stocks_return <- cbind(stocks$Dates, subset(stocks[,13:ncol(stocks)]))
stocks_return <- stocks_return[-1,]
cov(stocks_return[,2:12])

corr <- cor(stocks_return[,2:12])
ggcorrplot(corr, hc.order = TRUE, type = "lower",
           outline.col = "white", lab = TRUE)

```

Get the risk free rate
```{r}
# 10-year eurozone central governement bond yield interception date 1st. Feb 2017
rf_yield <- 0.00513337
rf_daily <- exp(rf_yield/365) -1
print(rf_daily) # 0.001881055
```

Compute market preimum
```{r}
stocks_return$mkt_premium <- NA

for (i in 1:length(stocks_return$`stocks$Dates`)) {
  stocks_return$mkt_premium[i] <- stocks_return$BM_return[i] - rf_daily
}

mkt_premium <- stocks_return$mkt_premium
```

Fit regression line to 10 individual stocks to get estimated parameters
```{r}
#regression GFC
gfc <- stocks_return$GFC_return - rf_daily
model1 <- lm(gfc~mkt_premium)
summary(model1)
#regression ENX
enx <- stocks_return$ENX_return - rf_daily
model2 <- lm(enx~mkt_premium)
summary(model2)

#regression BB
bic <- stocks_return$BB_return - rf_daily
model3 <- lm(bic~mkt_premium)
summary(model3)

#regression AD
ad <- stocks_return$AD_return - rf_daily
model4 <-lm(ad~mkt_premium)
summary(model4)

#regression ACA
aca <- stocks_return$ACA_return - rf_daily
model5 <- lm(aca~mkt_premium)
summary(model5)

#regression UPM
upm <- stocks_return$UPM_return- rf_daily
model6 <- lm(upm~mkt_premium)
summary(model6)

#regression KRC
krc <- stocks_return$KCR_return- rf_daily
model7 <- lm(krc~mkt_premium)
summary(model7)

#regression STREV
strev <- stocks_return$STREV_return - rf_daily
model8 <- lm(strev~mkt_premium)
summary(model8)

#regression CAI
cai <- stocks_return$CAI_return - rf_daily
model9 <- lm(cai~mkt_premium)
summary(model9)

#regression HBRN
hbrn <- stocks_return$HBRN_return - rf_daily
model10 <- lm(hbrn~mkt_premium)
summary(model10)

alpha <- c(model1$coefficients[1], model2$coefficients[1], model3$coefficients[1], 
         model4$coefficients[1], model5$coefficients[1], model6$coefficients[1], model7$coefficients[1], model8$coefficients[1], 
         model9$coefficients[1], model10$coefficients[1])
beta <- c(model1$coefficients[2], model2$coefficients[2], model3$coefficients[2], 
          model4$coefficients[2], model5$coefficients[2], model6$coefficients[2], model7$coefficients[2], model8$coefficients[2], 
          model9$coefficients[2], model10$coefficients[2])
residual_error <- c(summary(model1)$sigma, summary(model2)$sigma,summary(model3)$sigma,summary(model4)$sigma,summary(model5)$sigma,
                    summary(model6)$sigma,summary(model7)$sigma,summary(model8)$sigma,summary(model9)$sigma,summary(model10)$sigma)
a <- data.frame(alpha,beta, residual_error)
row.names(a) <- c("GFC","ENX","BB","AD","ACA","UPM","KRC","STREV","CAI","HBRN")
print(a)
```

###construct optimal portfolio
alpha = 0.001239429
beta =  0.7063661
```{r}
a$alpha_residual <- NA

for (i in 1:nrow(a)) {
  a$alpha_residual[i] <- a$alpha[i]/(a$residual_error[i])^2
}
print(a)

sum <- sum(a[,4])

#compute weight of each stock in the active portfolio
a$weight <- NA
for (i in 1:nrow(a)) {
  a$weight[i] <- a$alpha_residual[i]/sum
}
print(a)

#portfolio alpha
alpha_p <- NA

for (i in 1:(nrow(a))) {
  alpha_p[i] <- a$alpha[i]*a$weight[i]
}

alpha_p <- sum(alpha_p)
print(alpha_p) #alpha_p : 0.001246822

#portfolio beta
beta_p <- NA

for (i in 1:(nrow(a))) {
  beta_p[i] <- a$beta[i]*a$weight[i]
}

beta_p <- sum(beta_p)
print(beta_p) #beta_p : 0.8597035

```
##performance analysis
###optimal weighted portfolio
```{r}
library(readr)
performance_track <- read_csv("/Users/yuning/Documents/T3/Portfolio Management/performance_track.csv", 
                                  col_types = cols(ACA_return = col_number(), 
                                                            AD_return = col_number(), BB_return = col_number(), 
                                                           CAI_Return = col_number(), Dates = col_date(format = "%m/%d/%Y"), 
                                                           ENX_return = col_number(), GFC_return = col_number(), 
                                                           HBRN_return = col_number(), KCR_return = col_number(), 
                                                          STREV_return = col_number(), UPM_return = col_number()))
View(performance_track)

```

compute variance and volatility of the portfolio
```{r}
cov1 <- cov(performance_track[,2:11])
weight <- as.vector(a$weight) 
var_p <- t(weight)%*%cov1%*%weight
var_p  #var(p) : 9.913014e-05

sd_p <- sqrt(var_p)
sd_p # sd(p) : 0.00995641
```

portfolio's daily return
```{r}
return_p <- t(weight)%*%t(performance_track[,2:11])
return_p1 <- as.data.frame(t(return_p))
row.names(return_p1) <- c(performance_track$Dates)
colnames(return_p1) <- c("daily return")
return_p1
```

risk-free interest rate 1st march 2018
```{r}
rf_yield1 <- 0.0068594
rf_daily1 <- exp(rf_yield1/365) -1
rf_daily1
ret_p <- return_p1$`daily return` - rf_daily1
```

compute portfolio alpha and beta
```{r}
performance_track$mkt_premium1 <- NA

for (i in 1:length(performance_track$Dates)) {
  performance_track$mkt_premium1[i] <- performance_track$BM_return[i] - rf_daily1
}

mkt_premium1 <- performance_track$mkt_premium1

#regression 
model11 <- lm(ret_p~mkt_premium1)
summary(model11) # alpha =  0.0010177, beta = 0.6705805
```

compute TE, SR, IR
```{r}
#compute tracking error
track_error <- sqrt(var(return_p1$`daily return` - performance_track$BM_return))
track_error # tracking error = 0.008677862

#compute correlaton coefficient
b <- cbind(performance_track$BM_return, return_p1$`daily return`)
colnames(b) <- c("benchmark", "portfolio1")
rownames(b) <- c(performance_track$Dates)
cor(b) #correlaton = 0.562838

#compute sharpe ratio
SR <- (mean(return_p1$`daily return`) - rf_daily)/ sd_p
SR #SR = -0.01387756

#compute information ratio
IR <- (mean(mean(return_p1$`daily return`) - mean(performance_track$BM_return)) )/ track_error
IR #IR = 0.1439755
```

###equally weighted portfolio
daily return, variance and volatility
```{r}
weight_equal <- c(0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1)
return_p2 <- t(weight_equal)%*%t(performance_track[,2:11])
return_p2 <- as.data.frame(t(return_p2))
row.names(return_p2) <- c(performance_track$Dates)
colnames(return_p2) <- c("daily return")
return_p2

var(return_p2$`daily return`) # var = 4.155637e-05
sqrt(var(return_p2$`daily return`))
```

compute portfolio alpha and beta
```{r}
ret_p2 <- return_p2$`daily return` - rf_daily

#regression 
model12 <- lm(ret_p2~mkt_premium1)
summary(model12) # alpha = 0.0004304, beta = 0.5666197
```

compute TE, SR, IR
```{r}
#compute tracking error
track_error2 <- sqrt(var(return_p2$`daily return`- performance_track$BM_return))
track_error2 # tracking error = 0.005679053

#compute correlaton coefficient
c <- cbind(performance_track$BM_return, return_p2$`daily return`)
colnames(c) <- c("benchmark", "portfolio2")
rownames(c) <- c(performance_track$Dates)
cor(c) #correlaton = 0.7345278

#compute sharpe ratio
SR2 <- (mean(return_p2$`daily return`) - rf_daily)/ sd_p
SR2 #SR = 0.003007479

#compute information ratio
IR2 <- (mean(mean(return_p1$`daily return`) - mean(performance_track$BM_return)) )/ track_error2
IR2 #IR = 0.1018504

#compute sharpe ratio of the bm
SR3 <- (mean(performance_track$BM_return)- rf_daily) / sd(performance_track$BM_return)
SR3 
```

##performance comparison

daily return, daily return plot, correlation of securities
```{r}
require("ggplot2")

d <- cbind.data.frame(return_p1$`daily return`, return_p2$`daily return`, performance_track$BM_return)
colnames(d) <- c("portfolio_opt", "portfolio_equ","benchmark")
row.names(d) <- c(performance_track$Dates)
d
Date <- performance_track$Dates
Return <- d$portfolio_opt
ggplot(d, aes(Date)) + 
  geom_line(aes(y = Return, colour = "portfolio_opt")) + 
  geom_line(aes(y = portfolio_equ, colour = "portfolio_equ")) +
  geom_line(aes(y = benchmark, color ="benchmark"))

# correlation between each component in the portfolio.
library(ggcorrplot)
corr2 <- cor(performance_track[,2:12])
ggcorrplot(corr2, hc.order = TRUE, type = "lower",
           outline.col = "white", lab = TRUE)

```
